% GLOSSARY

%\newglossaryentry{<label>}{
%  name={<list entry>},  % the term
%  text={<entry as displayed in report text>},  % optional
%  description={<long description of the entry>} % brief description
%  plural={<entry in plural>} % entry in plural, only used if plural is not just -s
%}

% COMMANDS to use in the report to include the entry
%\gls{<label>} 
%\glspl{<label>} % for plural
%\Gls{<label>}   % capitalized
%\Glspl{<label>} % capitalized plural

\newglossaryentry{bid_strategy}
{name=bidding strategy,
 description={Systematic method to follow when bidding electricity production into the spot market (Elspot).},
 plural={bidding strategies}
}

\newglossaryentry{elspot}
{name=Elspot,
description={Day-ahead energy market. Bids on production volumes for each hour the following day are bid to Elspot at noon every day and auctioned by the TSO. The Elspot is a sub-market of the Nord Pool Spot.},
}

\newglossaryentry{nordpool}
{name=Nord Pool Spot,
description={Common power trading place for the Nordic and Baltic countries.},
}

\newglossaryentry{reg_market}
{name=regulating market,
description={The TSO's tool to balance power demand and supply, by activation of regulating bids. Only deterministic producers can bid into the regulating market.},
}

\newglossaryentry{nois_list}
{name=NOIS list,
description={The NOIS list contains the bids of the regulating market.},
}

\newglossaryentry{bal_market}
{name=balancing market,
description={A passive market which all players in the energy market are part of. Deviations in energy production vs. day-ahead bid are penalized in the balancing market according to the prices settled in the regulating market.},
}

\newglossaryentry{wind_power_penetration}
{name=wind power penetration,
description={The ratio between the produced amount of wind power in a given hour and the consumed amount of power in that same hour. Large wind power penetration corresponds to wind power covering a large amount of the energy consumed.},
}




